Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-15 batchdedup/eval.tex
updated scales on graphs

\todo{The names of the algorithms are just the temporary names I've been using for coding, DBP2 is the relative of the dual bin packing algorithm, BPL is the machine by machine largest VM to shortest round algorithm}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Total Jobspan (m)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y expr=(\thisrow{DBP2jobspan})/60] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{BPLjobspan})/60] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Jobspan for DBP2 and BPL}
  \label{fig:jobspan-comparison}
\end{figure}

>>>>

\todo{The names of the algorithms are just the temporary names I've been using for coding, DBP2 is the relative of the dual bin packing algorithm, BPL is the machine by machine largest VM to shortest round algorithm}
\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Total Jobspan (hrs)},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                %legend pos=north west
		]
                \addplot table[x=Rounds,y expr=(\thisrow{DBP2jobspan})/3600] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{BPLjobspan})/3600] {figures/packing_comparison.txt};
                \legend{DBP2, BPL};
		\end{axis}
	\end{tikzpicture}
  \caption{Jobspan for DBP2 and BPL}
  \label{fig:jobspan-comparison}
\end{figure}
